Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web

### 2025-05-07 autovi_paper.qmd
Improve the second paragraph

However, relying solely on subjective assessments of these plots can lead to issues such as over-interpreting random patterns as model violations. @li2024plot demonstrated that visual methods using the lineup protocol [@buja2009statistical] for assessing residuals are more useful, and also perform more practically than conventional tests due to their reduced sensitivity to minor departures. Packages such as `nullabor` [@nullabor], `HLMdiag` [@loy2014hlmdiag], and `regressinator` [@regressinator], enable users to compare observed residual plots with plots of samples from null distributions, helping to quantify the significance of any detected patterns.

>>>>

However, relying solely on subjective assessments of these plots can lead to issues such as over-interpreting random patterns as model violations. @li2024plot demonstrated that visual inference methods, particularly those using the lineup protocol [@buja2009statistical], offer more practical and reliable assessments of residual patterns than conventional tests, as they are less sensitive to minor departures. Packages such as `nullabor` [@nullabor], `HLMdiag` [@loy2014hlmdiag], and `regressinator` [@regressinator] support this approach by enabling users to compare observed residual plots with plots generated under null hypothesis, thereby helping to quantify the significance of any detected patterns.

### 2025-05-07 autovi_paper.tex
Improve the second paragraph

However, relying solely on subjective assessments of these plots can
lead to issues such as over-interpreting random patterns as model
violations. \citet{li2024plot} demonstrated that visual methods using
the lineup protocol \citep{buja2009statistical} for assessing residuals
are more useful, and also perform more practically than conventional
tests due to their reduced sensitivity to minor departures. Packages
such as \texttt{nullabor} \citep{nullabor}, \texttt{HLMdiag}
\citep{loy2014hlmdiag}, and \texttt{regressinator}
\citep{regressinator}, enable users to compare observed residual plots
with plots of samples from null distributions, helping to quantify the
significance of any detected patterns.

>>>>

However, relying solely on subjective assessments of these plots can
lead to issues such as over-interpreting random patterns as model
violations. \citet{li2024plot} demonstrated that visual inference
methods, particularly those using the lineup protocol
\citep{buja2009statistical}, offer more practical and reliable
assessments of residual patterns than conventional tests, as they are
less sensitive to minor departures. Packages such as \texttt{nullabor}
\citep{nullabor}, \texttt{HLMdiag} \citep{loy2014hlmdiag}, and
\texttt{regressinator} \citep{regressinator} support this approach by
enabling users to compare observed residual plots with plots generated
under null hypothesis, thereby helping to quantify the significance of
any detected patterns.
